Understanding domestic abuse

### 2019-07-23 JeS_fields.tex

Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first comprehensive, quantitative UK-based investigation of the individual and environmental predictors of domestic abuse victimisation. Previous investigations focusing on domestic abuse in the context of the UK have either exclusively relied on police records or used a small-sample, qualitative approach. By drawing on multiple data sources, including police crime data and the CSEW, we can combine their strengths to validate previous findings and deliver new insights.

@@

Criminologists working on exploring the experiences of domestic abuse survivors in the Criminal Justice System will benefit from our research examining whether police mis-recording disproportionately affects certain victim groups.

>>>>

Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first comprehensive, quantitative UK-based investigation of the individual and environmental predictors of domestic abuse victimisation. Previous investigations focusing on domestic abuse in the context of the UK have either exclusively relied on police records or used a small-sample, qualitative approach. By drawing on multiple data sources, including police crime data and the CSEW, we can combine their strengths to validate previous findings and deliver new insights stimulating future research efforts.

@@

Criminologists working on exploring the experiences of domestic abuse survivors in the Criminal Justice System will benefit from our research examining whether police mis-recording disproportionately affects certain victim groups, and its implications for victim's trust in the CJS.
